PLANETESIMAL ACCRETION AT SHORT ORBITAL PERIODS

### 2023-01-04 main.tex
Fill in acknowledgements

\documentclass[twocolumn]{aastex63}
\usepackage{natbib}
%\definecolor{orcidlogocol}{HTML}{A6CE39}
\bibliographystyle{aasjournal}

@@

\section{Acknowledgements}

NSF, XSEDE.

>>>>

\documentclass[twocolumn,linenumbers]{aastex63}
\usepackage{natbib}
%\definecolor{orcidlogocol}{HTML}{A6CE39}
\bibliographystyle{aasjournal}

@@

\section*{Acknowledgements}
The simulations presented in this work were run on XSEDE/SDSC Comet and Expanse under allocation MCA94P018. SCW and TRQ were were supported by NSF award 62-2684. We acknowledge the people of the Dkhw’Duw’Absh, the Duwamish Tribe, the Muckleshoot Tribe, and other tribes on whose traditional lands we have performed this work.

\textit{Software:} Astropy \citep{astropy13}, {\sc ChaNGa} \citep{jetley08, menon15}, Matplotlib 
\citep{matplotlib07}, NumPy \citep{numpy11}, Pandas \citep{pandas10}, {\sc PYNBODY} \citep{pynbody13}

\section*{Data Availability}
The data presented in this article are available on our GitHub repository, at \url{https://github.com/spencerw/stip_planetesimal_paper}.
